The very dependent recursive structure of iterated parametricity in indexed form

### 2025-12-22 paper/paper.tex
paper, tab-frames: work on consistency, fixing errors

Table~\ref{tab:coind} describes the type of a $\nu$-set at level $m$ as a dependent stream of type families representing the limit of $n$-truncated $\nu$-sets: the recursive equation $\Xfrom{m}{n}{D} \,\defeq\, \Sigma R: \Xcomp{m}{n}[D=\D].\, \Xfrom{m}{n+1}[D=\pair{D}{R}]$ from the table formally corresponds to the stream $Stream_{\Sigma n.\, \Xto{m}{n},\, \lambda (n, \D).\, \Xcomp{m}{n}[D=\D],\,\lambda ((n, D),R).(n+1,(\pair{D}{R}))}(n, \D)$. Therefore, $\Xfrom{m}{n}$ denotes an infinite sequence $X_{n}, X_{n+1}, \ldots$ dependent on a $(<n)$-truncated $\nu$-set, $\Xto{m}{n}$, so that, when $n$ is $0$, it denotes a full $\nu$-set, written $\Xp{m}$. This is made possible because the $(<0)$-truncated $\nu$-set, $\Xto{m}{0}$, is degenerated: it is an empty family, and there is thus only one $(<0)$-truncated $\nu$-set, namely the canonical inhabitant $\kstar$ of $\unittype$.

@@

Since $\restrf[n][p]$ is referring to $\framep[n][p]$ and $\framep[n-1][p]$, and $\cohf[n][p]$ is referring to $\restrf[n][p]$ and $\restrf[n-1][p]$, thus also to $\framep[n][p]$, $\framep[n-1][p]$ and $\framep[n-2][p]$, we built all of these 6 components at the same time. But equations were also needed to state the properties of $\framep[n][p]$, $\framep[n-1][p]$ and $\restrf[n][p]$ so that we were building by induction on $n+p$ (that is on $n$, using the convention of \cite{hr25}), for any $D:\Xto{m}{n}$, the following block of information:

@@

\begin{align*}
  \framep[n][p]   & : \U                                                                                                        & \mbox{for all $p\leq n$} \\
  \painting[n][p] & : \framep[n][p] \rightarrow \U                                                                              & \mbox{for all $p\leq n$} \\
  \restrf[n][p]   & : \Pi q \leq n+p.\, \Pi \epsilon.\, \framep[n+1][p] \rightarrow \framep[n][p]                               & \mbox{for all $p\leq n$} \\
  \restrp[n][p]   & : \Pi q \leq n+p.\, \Pi \epsilon.\, \Pi d:\framep[n+1][p].\,                                                                           \\
                  & \;\;\;\;\painting[n+1][p](d) \rightarrow \painting[n][p](\restrf[n][p](d))                                  & \mbox{for all $p\leq n$} \\
  \cohf[n][p]     & : \Pi qr\epsilon\omega.\, \restrf[n][p][\epsilon][q] \circ \restrf[n+1][p][\omega][r] =                                                \\
                  & \;\;\;\;\restrf[n][p][\omega][r] \circ \restrf[n+1][p][\epsilon][q+1]                                       & \mbox{for all $p\leq n$} \\
  \cohp[n][p]     & \Pi qr\epsilon\omega.\,\Pi d:\framep[n+2][p].\,                                                                                        \\
                  & \;\;\;\;\restrp[n][p][q][\epsilon](\restrf[n+1][p][r][\omega](d)) \circ \restrp[n+1][p][r][\omega](d) =                                \\
                  & \;\;\;\;\restrp[n][p][r][\omega](\restrf[n+1][p][q+1][\epsilon](d)) \circ \restrp[n+1][p][q+1][\epsilon](d) & \mbox{for all $p\leq n$} \\
\end{align*}

@@

The definition of $\framep[n+1][p]$ also depends, via $\layer[n][p-1]$, on $\painting[n][p-1]$. Both via $\painting[n][p-1]$ and $\restrf[n][p-1]$, it depends also on $\framep[n][p-1]$ by typing dependency. This requires to assume $\framep[n][p-1]$ and $\painting[n][p-1]$ known in advance.
Moreover, the definition of $\framep[n+1][p]$ depends on $\framep[n+1][p-1]$, so all of $\framep[n][k]$, $\painting[n][k]$ and $\restrf[n][k]$ for $k< p$ need to be known, which we respectively abbreviate as $\framep[n][\lbrack 0,p-1 \rbrack]$, $\painting[n][\lbrack 0,p-1 \rbrack]$ and $\restrf[n][p-1]$.
Schematically, using dotted arrows for dependencies in the type and plain arrows for dependencies in the definition, this gives the following dependencies for $p\leq n+1$ fixed:
\begin{center}
  \fontsize{7.2}{9}\selectfont
  \begin{tikzcd}
    \framep[n+1][\lbrack 0,p \rbrack] \arrow[d] \arrow[ddr]\\
    \painting[n][\lbrack 0,p-1 \rbrack] \arrow[d, dotted] \\
    \framep[n][\lbrack 0,p-1 \rbrack] &
    \restrf[n][\lbrack 0,p-1 \rbrack] \arrow[l, dotted] \arrow[uul, dotted, "\mbox{$[\lbrack 0,p-1 \rbrack]$}"', near start, shift right=2mm, hook']\\
  \end{tikzcd}
\end{center}

@@

So far, using this recursive definition of  $\framep[n][\lbrack 0,p-1 \rbrack]$ and $\restrf[n][\lbrack 0,p-1 \rbrack]$, we are able to specify the three first component of the exected dependent structure:
\begin{align*}
  \framep[n][p]             & : \U                                & \mbox{for all $p\leq n$} \\
  \painting[n][p]           & : \framep[n][p] \rightarrow \U      & \mbox{for all $p\leq n$} \\
  \restrf[n][p]             & : \Pi q \leq n+p.\, \framep[n+1][p]
  \left(\begin{array}{l}
            \framep[n][\lbrack 0,p-1 \rbrack]   \\
            \painting[n][\lbrack 0,p-1 \rbrack] \\
            \restrf[n][\lbrack 0,p-1 \rbrack]   \\
          \end{array}\right)
  \rightarrow \framep[n][p] & \mbox{for all $p\leq n$}                                       \\
\end{align*}
which can appropriately be reformulated using sequences for appropriate definitions of $\frametype[n][\lbrack 0,p \rbrack]$, $\paintingtype[n][\lbrack 0,p \rbrack]$ and $\restrftype[n][\lbrack 0,p \rbrack]$, since the dependencies of $\restrf[n][p]$ into $\restrf[n][\lbrack 0,p-1 \rbrack]$ makes it a very dependent function~\citep{Hickey96}:
\begin{align*}
  \framep[n][\lbrack 0,p \rbrack]   & : \frametype[n][\lbrack 0,p \rbrack]                                     \\
  \painting[n][\lbrack 0,p \rbrack] & : \paintingtype[n][\lbrack 0,p \rbrack](\framep[n][\lbrack 0,p \rbrack]) \\
  \restrf[n][\lbrack 0,p \rbrack]   & : \restrftype[n][\lbrack 0,p \rbrack]
  \left(\begin{array}{l}
            \framep[n][\lbrack 0,p-1 \rbrack]   \\
            \painting[n][\lbrack 0,p-1 \rbrack] \\
            \restrf[n][\lbrack 0,p-1 \rbrack]   \\
          \end{array}\right)                                                                    \\
\end{align*}

@@

\begin{equation*}
  \fontsize{7.2}{9}\selectfont
  \begin{array}{llcl}
    \frametype[n][\lbrack 0,p-1 \rbrack] &  & :      & \U                                               \\
    \frametype[n][\lbrack \rbrack]       &  & \defeq & \unittype                                        \\
    \frametype[n][\lbrack 0,p \rbrack]   &  & \defeq & \frametype[n+1][\lbrack 0,p-1 \rbrack] \times \U \\
  \end{array}
\end{equation*}

@@

\begin{equation*}
  \fontsize{7.2}{9}\selectfont
  \begin{array}{llcl}
    \paintingtype[n][\lbrack 0,p-1 \rbrack] & (\framep[n][\lbrack 0,p \rbrack]:\frametype[n][\lbrack 0,p-1 \rbrack]) & :      & \U                                                                                                                   \\
    \paintingtype[n][\lbrack \rbrack]       & \unitpoint                                                             & \defeq & \unittype                                                                                                            \\
    \paintingtype[n][\lbrack 0,p \rbrack]   & (\framep[n][\lbrack 0,p \rbrack])                                      & \defeq & \paintingtype[n+1][\lbrack 0,p-1 \rbrack](\framep[n+1][\lbrack 0,p-1 \rbrack]) \times (\framep[n][p] \rightarrow \U) \\
  \end{array}
\end{equation*}

@@

    \restrftype[n][\lbrack 0,0-1 \rbrack]     &

@@

    \restrftype[n][\lbrack 0,(p+1)-1 \rbrack] &

@@

      \Pi q\leq n.\,\Pi \omega.\,\framep[n+1][p]

@@

    d \mapsto \Pi\omega.\,\painting[n][p](\deps.\restrf[n][p][0][\omega](d))                                             \\

@@

Note that we write $\deps.\framep$, $\deps.\painting$, $\deps.\restrf$ for the
projections of a $\deps$. Also, by abuse of notation, we write $\unitpoint$ for
the only inhabitant of $\depstype[n][\lbrack 0,0-1 \rbrack]$.

@@

We can now formally define $\painting[n+1][p]$ by recursion on $n+1-p$:
\begin{equation*}
  \fontsize{7.2}{9}\selectfont
  \begin{array}{llcl}
    \painting[n+1][p]          &
    (\fulldeps[n]:\fulldepstype[n])                                       \\
    \painting[n+1][n+1]        &
    \fulldeps[n]               & \defeq & \fulldeps.E                     \\
    \painting[n+1][p](p\leq n) &
    \fulldeps[n]               & \defeq & d \mapsto
    \left(\begin{array}{l}
              \Sigma l:\layer[n][p](\fulldeps.\deps[n][\lbrack 0,p \rbrack]). \\
              \painting[n+1][p+1]
              (\fulldeps[n])(d,l)                                             \\
            \end{array}\right) \\
  \end{array}
\end{equation*}

@@

\begin{equation*}
  \fontsize{7.2}{9}\selectfont
  \begin{array}{llcl}
    \painting[n+1][\lbrack 0,p-1 \rbrack] &
    (\fulldeps[n]:\fulldepstype[n])       & :      & \paintingtype[n+1][\lbrack 0,p-1 \rbrack](\framep[n+1][\lbrack 0,p-1 \rbrack](\fulldeps.\deps[n][\lbrack 0,p-1 \rbrack])) \\
    \painting[n+1][\lbrack \rbrack]       &
    \fulldeps[n]                          & \defeq & \unittype                                                                                                                 \\
    \painting[n+1][\lbrack 0,p \rbrack]   &
    \fulldeps[n]
                                          & \defeq &
    (\painting[n+1][\lbrack 0,p-1 \rbrack](\fulldeps[n-1]),\painting[n+1][p](\fulldeps[n]))                                                                                    \\
  \end{array}
\end{equation*}

@@

\begin{equation*}
  \fontsize{7.2}{9}\selectfont
  \begin{array}{llcl}
    \restrptype[n][\lbrack 0,p-1 \rbrack] &
    (\fulldeps[n]:\fulldepstype[n])       & :      & \U                                                                \\
    \restrptype[n][\lbrack \rbrack]       & E      & \defeq                                                & \unittype \\
    \restrptype[n][\lbrack 0,p \rbrack]   &
    (\fulldeps[n])
                                          & \defeq & \restrptype[n+1][\lbrack 0,p-1 \rbrack] \times \left(
    \begin{array}{l}
        \Pi q\leq n.\Pi \epsilon.\Pi d:\framep[n+1][p](\fulldeps.\deps[n][\lbrack 0,p-1 \rbrack]). \\
        \painting[n+1][p]
        (\fulldeps[n])(d) \rightarrow                                                              \\ \fulldeps.\deps.\painting[n][p](\fulldeps.\deps.\restrf[n][p][q][\epsilon](d))\end{array}
    \right)                                                                                                            \\
  \end{array}
\end{equation*}

@@

    \cohftype[n][\lbrack \rbrack]           &

@@

             \Pi q\leq n.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega.\,\Pi d:\framep[n+2][p]

@@

             \Pi q \leq n. \Pi \epsilon. \Pi d: \framep[n+2][p](\overline{\deps}(\depscohs[n][\lbrack 0,p-1 \rbrack])).\, \\

@@

    \lambda q\leq n. \lambda \epsilon.\,\lambda d.\lambda l.\overrightarrow{\cohf[n][p][q][q][\epsilon][\omega](d)}{\restrp[n][p][q][\epsilon](\restrf[n][p][q][\epsilon](\depscohs[n][\lbrack 0,p-1 \rbrack])(d))(l \omega)} \\

@@

By abuse of notation, we also write $E$ for an inhabitant of $\depscohstype[n][\lbrack 0,0-1 \rbrack]$ (standing for a non trivial inhabitant of $\fulldeps[n]$).

@@

\begin{equation*}
  \fontsize{7.2}{9}\selectfont
  \begin{array}{llcl}
    \restrp[n+1][p]                         &
    (\fulldepscohs[n]:\fulldepscohstype[n]) & :      &
    \left(
    \begin{array}{l}
        \Pi q\leq n. \Pi \epsilon. \Pi d:\framep[n+2][p]
        (\overline{\deps}(\fulldepscohs.\depscohs[n][\lbrack 0,p-1 \rbrack])). \\
        \painting[n+2][p]
        (\overline{\fulldeps}(\fulldepscohs[n]))(d) \rightarrow                \\
        \painting[n+1][p](\fulldepscohs.\depscohs.\fulldeps[n])
        (\restrf[n+1][p](\fulldepscohs.\depscohs[n][\lbrack 0,p-1 \rbrack])(d))\end{array}\right)                                                        \\
    \restrp[n+1][n+1]                       &
    (\fulldepscohs[n])                      & \defeq & \lambda q\leq n.\lambda \epsilon. \lambda d. \lambda (l,c). l\epsilon \\
    \restrp[n+1][p](p\leq n)                &
    (\fulldepscohs[n])                      & \defeq & \lambda q\leq n.\lambda \epsilon. \lambda d. \lambda (l,c).
    \left(\begin{array}{l}
              \restrl[n][p][q][\epsilon](\fulldepscohs.\depscohs[n][\lbrack 0,p \rbrack])(d)(l), \\
              \restrp[n+1][p+1][q][\epsilon](\fulldepscohs[n])(d,l)(c)                           \\
            \end{array}\right)                                 \\
  \end{array}
\end{equation*}

@@

\begin{equation*}
  \fontsize{7.2}{9}\selectfont
  \begin{array}{llcl}
    \restrp[n+1][\lbrack 0,p-1 \rbrack]     &
    (\fulldepscohs[n]:\fulldepscohstype[n]) & :      & \restrptype[n+1][\lbrack 0,p-1 \rbrack](\fulldepscohs.\depscohs.\fulldeps[n])) \\
    \restrp[n+1][\lbrack \rbrack]           &
    \fulldepscohs[n]                        & \defeq & \unittype                                                                      \\
    \restrp[n+1][\lbrack 0,p \rbrack]       &
    \fulldepscohs[n]
                                            & \defeq &
    (\restrp[n+1][\lbrack 0,p-1 \rbrack](\fulldepscohs[n]),\restrp[n+1][p](\fulldepscohs[n]))                                         \\
  \end{array}
\end{equation*}

@@

\begin{equation*}
  \fontsize{7.2}{9}\selectfont
  \begin{array}{llcl}
    \cohptype[n][\lbrack 0,p-1 \rbrack]     & (\fulldepscohs[n]:\fulldepscohstype[n]) & :      & \U                                                           \\
    \cohptype[n][\lbrack 0,0-1 \rbrack]     & \unitpoint                              & \defeq & \unittype                                                    \\
    \cohptype[n][\lbrack 0,(p+1)-1 \rbrack] & (\fulldepscohs[n])                      & \defeq & \cohptype[n][\lbrack 0,p-1 \rbrack](\fulldepscohs[n]) \times \\
                                            &                                         &        & \;\;\;\;\left\{
    \begin{array}{l}
      \Pi q\leq n.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega.\,\Pi d:\framep[n+2][p](\overline{\deps}(\fulldepscohs.\depscohs[n][\lbrack 0,p-1 \rbrack])).\,\Pi c:\painting[n+2][p](\overline{\fulldeps}(\fulldepscohs[n])) \\
      \fulldepscohs.\depscohs.\restrp[n][p][q][\epsilon](\restrf[n+1][p](d))(\restrp[n+1][p][r][\omega]
      (\fulldepscohs[n])(d)(c)) =                                                                                                                                                                                          \\
      \fulldepscohs.\depscohs.\restrp[n][p][r][\omega](\restrf[n+1][p](d))(\restrp[n+1][p][q+1][\epsilon]
      (\fulldepscohs[n])(d)(c))
    \end{array}
    \right.                                                                                                                                                   \\
  \end{array}
\end{equation*}

@@

    \cohttype[n][\lbrack \rbrack]                                                            &

@@

              \Pi q\leq n.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega.\,\Pi \theta.\, \\

@@

      \Pi q\leq n.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega.                                                                             \\

@@

The last key construction we need is $\cohp[n+1][p]$, which is by recursion on $n-p$:

>>>>

Table~\ref{tab:coind} describes the type of a $\nu$-set at level $m$ as a dependent stream of type families representing the limit of $n$-truncated $\nu$-sets: the recursive equation $\Xfrom{m}{n}{D} \,\defeq\, \Sigma R: \Xcomp{m}{n}[D=\D].\, \Xfrom{m}{n+1}[D=\pair{D}{R}]$ from the table formally corresponds to the stream $Stream_{\Sigma n.\, \Xto{m}{n},\, \lambda (n, \D).\, \Xcomp{m}{n}[D=\D],\,\lambda ((n, D),R).(n+1,(\pair{D}{R}))}(n, \D)$. Therefore, $\Xfrom{m}{n}$ denotes an infinite sequence $X_{n}, X_{n+1}, \ldots$ dependent on a $(<n)$-truncated $\nu$-set, $\Xto{m}{n}$, so that, when $n$ is $0$, it denotes a full $\nu$-set, written $\Xp{m}$. This is made possible because the $(<0)$-truncated $\nu$-set, $\Xto{m}\lbrack 0,0 \rbrack$, is degenerated: it is an empty family, and there is thus only one $(<0)$-truncated $\nu$-set, namely the canonical inhabitant $\kstar$ of $\unittype$.

@@

Since $\restrf[n][p]$ is referring to $\framep[n][p]$ and $\framep[n-1][p]$, and $\cohf[n][p]$ is referring to $\restrf[n][p]$ and $\restrf[n-1][p]$, thus also to $\framep[n][p]$, $\framep[n-1][p]$ and $\framep[n-2][p]$, we built all of these 6 components at the same time. But equations were also needed to state the properties of $\framep[n][p]$, $\framep[n-1][p]$ and $\restrf[n][p]$ so that we were building by induction on $n$, for any $D:\Xto{m}{n}$, the following block of information:

@@

\begin{align*}
  \framep[n][p]   & : \U                                                                                                        & \mbox{for all $p\leq n$} \\
  \painting[n][p] & : \framep[n][p] \rightarrow \U                                                                              & \mbox{for all $p\leq n$} \\
  \restrf[n][p]   & : \Pi q \leq n-p.\, \Pi \epsilon.\, \framep[n+1][p] \rightarrow \framep[n][p]                               & \mbox{for all $p\leq n$} \\
  \restrp[n][p]   & : \Pi q \leq n-p.\, \Pi \epsilon.\, \Pi d:\framep[n+1][p].\,                                                                           \\
                  & \;\;\;\;\painting[n+1][p](d) \rightarrow \painting[n][p](\restrf[n][p](d))                                  & \mbox{for all $p\leq n$} \\
  \cohf[n][p]     & : \Pi qr\epsilon\omega.\, \restrf[n][p][\epsilon][q] \circ \restrf[n+1][p][\omega][r] =                                                \\
                  & \;\;\;\;\restrf[n][p][\omega][r] \circ \restrf[n+1][p][\epsilon][q+1]                                       & \mbox{for all $p\leq n$} \\
  \cohp[n][p]     & \Pi qr\epsilon\omega.\,\Pi d:\framep[n+2][p].\,                                                                                        \\
                  & \;\;\;\;\restrp[n][p][q][\epsilon](\restrf[n+1][p][r][\omega](d)) \circ \restrp[n+1][p][r][\omega](d) =                                \\
                  & \;\;\;\;\restrp[n][p][r][\omega](\restrf[n+1][p][q+1][\epsilon](d)) \circ \restrp[n+1][p][q+1][\epsilon](d) & \mbox{for all $p\leq n$} \\
\end{align*}

@@

The definition of $\framep[n+1][p]$ also depends, via $\layer[n][p-1]$, on $\painting[n][p-1]$. Both via $\painting[n][p-1]$ and $\restrf[n][p-1]$, it depends also on $\framep[n][p-1]$ by typing dependency. This requires to assume $\framep[n][p-1]$ and $\painting[n][p-1]$ known in advance.
Moreover, the definition of $\framep[n+1][p]$ depends on $\framep[n+1][p-1]$, so all of $\framep[n][k]$, $\painting[n][k]$ and $\restrf[n][k]$ for $k< p$ need to be known, which we respectively abbreviate as $\framep[n][\lbrack 0,p-1 \rbrack]$, $\painting[n][\lbrack 0,p-1 \rbrack]$ and $\restrf[n][p-1]$.
Schematically, using dotted arrows for dependencies in the type and plain arrows for dependencies in the definition, this gives the following dependencies for $p\leq n+1$ fixed:
\begin{center}
  \fontsize{7.2}{9}\selectfont
  \begin{tikzcd}
    \framep[n+1][\lbrack 0,p \rbrack] \arrow[d] \arrow[ddr]\\
    \painting[n][\lbrack 0,p-1 \rbrack] \arrow[d, dotted] \\
    \framep[n][\lbrack 0,p-1 \rbrack] &
    \restrf[n][\lbrack 0,p-1 \rbrack] \arrow[l, dotted] \arrow[uul, dotted, "\mbox{$[0,p-1]$}"', near start, shift right=2mm, hook']\\
  \end{tikzcd}
\end{center}

@@

So far, using this recursive definition of  $\framep[n][\lbrack 0,p-1 \rbrack]$ and $\restrf[n][\lbrack 0,p-1 \rbrack]$, we are able to specify the three first component of the exected dependent structure:
\begin{align*}
  \framep[n][p]             & : \U                                               & \mbox{for all $p\leq n$} \\
  \painting[n][p]           & : \framep[n][p] \rightarrow \U                     & \mbox{for all $p\leq n$} \\
  \restrf[n][p]             & : \Pi q \leq n-p.\, Pi \epsilon.\, \framep[n+1][p]
  \left(\begin{array}{l}
            \framep[n][\lbrack 0,p-1 \rbrack]   \\
            \painting[n][\lbrack 0,p-1 \rbrack] \\
            \restrf[n][\lbrack 0,p-1 \rbrack]   \\
          \end{array}\right)
  \rightarrow \framep[n][p] & \mbox{for all $p\leq n$}                                                      \\
\end{align*}
which can appropriately be reformulated using sequences for appropriate definitions of $\frametype[n][\lbrack 0,p \rbrack]$, $\paintingtype[n][\lbrack 0,p \rbrack]$ and $\restrftype[n][\lbrack 0,p \rbrack]$, since the dependencies of $\restrf[n][p]$ into $\restrf[n][\lbrack 0,p-1 \rbrack]$ makes it a very dependent function~\citep{Hickey96}:
\begin{align*}
  \framep[n][\lbrack 0,p \rbrack]   & : \frametype[n][\lbrack 0,p \rbrack]                                     \\
  \painting[n][\lbrack 0,p \rbrack] & : \paintingtype[n][\lbrack 0,p \rbrack](\framep[n][\lbrack 0,p \rbrack]) \\
  \restrf[n][\lbrack 0,p \rbrack]   & : \restrftype[n][\lbrack 0,p \rbrack]
  \left(\begin{array}{l}
            \framep[n][\lbrack 0,p-1 \rbrack]   \\
            \painting[n][\lbrack 0,p-1 \rbrack] \\
            \restrf[n][\lbrack 0,p-1 \rbrack]   \\
          \end{array}\right)                                                                    \\
\end{align*}

@@

\begin{equation*}
  \fontsize{7.2}{9}\selectfont
  \begin{array}{llcl}
    \frametype[n][\lbrack 0,p-1 \rbrack] &  & :      & \U                                               \\
    \frametype[n]                        &  & \defeq & \unittype                                        \\
    \frametype[n][\lbrack 0,p \rbrack]   &  & \defeq & \frametype[n+1][\lbrack 0,p-1 \rbrack] \times \U \\
  \end{array}
\end{equation*}

@@

\begin{equation*}
  \fontsize{7.2}{9}\selectfont
  \begin{array}{llcl}
    \paintingtype[n][\lbrack 0,p-1 \rbrack] & (\framep[n][\lbrack 0,p \rbrack]:\frametype[n][\lbrack 0,p-1 \rbrack]) & :      & \U                                                                                                                   \\
    \paintingtype[n]                        & \unitpoint                                                             & \defeq & \unittype                                                                                                            \\
    \paintingtype[n][\lbrack 0,p \rbrack]   & (\framep[n][\lbrack 0,p \rbrack])                                      & \defeq & \paintingtype[n+1][\lbrack 0,p-1 \rbrack](\framep[n+1][\lbrack 0,p-1 \rbrack]) \times (\framep[n][p] \rightarrow \U) \\
  \end{array}
\end{equation*}

@@

    \restrftype[n]                        &

@@

    \restrftype[n][\lbrack 0,p \rbrack]   &

@@

      \Pi q \leq n-p.\,\Pi \epsilon.\,\framep[n+1][p]

@@

    d \mapsto \Pi\epsilon.\,\painting[n][p](\deps.\restrf[n][p][0][\epsilon](d))                                         \\

@@

Note that we write $\deps.\framep$, $\deps.\painting$, $\deps.\restrf$ for the
projections of a $\deps$. Also, by abuse of notation, we write $\unitpoint$ for
the only inhabitant of $\depstype[n]$.

@@

We can now formally define $\painting[n+1][p]$ for $p \leq n+1$ by recursion on $n-p$:
\begin{equation*}
  \fontsize{7.2}{9}\selectfont
  \begin{array}{llcl}
    \painting[n+1][p]               &
    (\fulldeps[n]:\fulldepstype[n]) & :      & \paintingtype[n+1][p]      \\
    \painting[n+1][n+1]             &
    \fulldeps[n]                    & \defeq & \fulldeps.E                \\
    \painting[n+1][p \leq n]        &
    \fulldeps[n]                    & \defeq & d \mapsto
    \left(\begin{array}{l}
              \Sigma l:\layer[n][p](\fulldeps.\deps[n][\lbrack 0,p \rbrack]). \\
              \painting[n+1][p+1]
              (\fulldeps[n])(d,l)                                             \\
            \end{array}\right) \\
  \end{array}
\end{equation*}

@@

\begin{equation*}
  \fontsize{7.2}{9}\selectfont
  \begin{array}{llcl}
    \painting[n+1][\lbrack 0,p-1 \rbrack] &
    (\fulldeps[n]:\fulldepstype[n])       & :      & \paintingtype[n+1][\lbrack 0,p-1 \rbrack](\framep[n+1][\lbrack 0,p-1 \rbrack](\fulldeps.\deps[n][\lbrack 0,p-1 \rbrack])) \\
    \painting[n+1]                        &
    \fulldeps[n]                          & \defeq & \unittype                                                                                                                 \\
    \painting[n+1][\lbrack 0,p \rbrack]   &
    \fulldeps[n]
                                          & \defeq &
    (\painting[n+1][\lbrack 0,p-1 \rbrack](\fulldeps[n-1]),\painting[n+1][p](\fulldeps[n]))                                                                                    \\
  \end{array}
\end{equation*}

@@

\begin{equation*}
  \fontsize{7.2}{9}\selectfont
  \begin{array}{llcl}
    \restrptype[n][\lbrack 0,p-1 \rbrack] &
    (\fulldeps[n]:\fulldepstype[n])       & :      & \U                                                                \\
    \restrptype[n]                        & E      & \defeq                                                & \unittype \\
    \restrptype[n][\lbrack 0,p \rbrack]   &
    (\fulldeps[n])
                                          & \defeq & \restrptype[n+1][\lbrack 0,p-1 \rbrack] \times \left(
    \begin{array}{l}
        \Pi q \leq n-p.\Pi \epsilon.\Pi d:\framep[n+1][p](\fulldeps.\deps[n][\lbrack 0,p-1 \rbrack]). \\
        \painting[n+1][p]
        (\fulldeps[n])(d) \rightarrow                                                                 \\ \fulldeps.\deps.\painting[n][p](\fulldeps.\deps.\restrf[n][p][q][\epsilon](d))\end{array}
    \right)                                                                                                            \\
  \end{array}
\end{equation*}

@@

    \cohftype[n]                            &

@@

             \Pi q \leq n-p.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega.\,\Pi d:\framep[n+2][p]

@@

             \Pi q \leq n-p. \Pi \epsilon. \Pi d: \framep[n+2][p](\overline{\deps}(\depscohs[n][\lbrack 0,p-1 \rbrack])).\, \\

@@

    \lambda q \leq n-p. \lambda \epsilon.\,\lambda d.\lambda l.\overrightarrow{\cohf[n][p][q][q][\epsilon][\omega](d)}{\restrp[n][p][q][\epsilon](\restrf[n][p][q][\epsilon](\depscohs[n][\lbrack 0,p-1 \rbrack])(d))(l \omega)} \\

@@

By abuse of notation, we also write $E$ for an inhabitant of $\depscohstype[n]$ (standing for a non trivial inhabitant of $\fulldeps[n]$).

@@

\begin{equation*}
  \fontsize{7.2}{9}\selectfont
  \begin{array}{llcl}
    \restrp[n+1][p]                         &
    (\fulldepscohs[n]:\fulldepscohstype[n]) & :      &
    \left(
    \begin{array}{l}
        \Pi q \leq n-p. \Pi \epsilon. \Pi d:\framep[n+2][p]
        (\overline{\deps}(\fulldepscohs.\depscohs[n][\lbrack 0,p-1 \rbrack])). \\
        \painting[n+2][p]
        (\overline{\fulldeps}(\fulldepscohs[n]))(d) \rightarrow                \\
        \painting[n+1][p](\fulldepscohs.\depscohs.\fulldeps[n])
        (\restrf[n+1][p](\fulldepscohs.\depscohs[n][\lbrack 0,p-1 \rbrack])(d))\end{array}\right)                                                           \\
    \restrp[n+1][n+1]                       &
    (\fulldepscohs[n])                      & \defeq & \lambda q \leq n-p.\lambda \epsilon. \lambda d. \lambda (l,c). l\epsilon \\
    \restrp[n+1][p \leq n]                  &
    (\fulldepscohs[n])                      & \defeq & \lambda q \leq n-p.\lambda \epsilon. \lambda d. \lambda (l,c).
    \left(\begin{array}{l}
              \restrl[n][p][q][\epsilon](\fulldepscohs.\depscohs[n][\lbrack 0,p \rbrack])(d)(l), \\
              \restrp[n+1][p+1][q][\epsilon](\fulldepscohs[n])(d,l)(c)                           \\
            \end{array}\right)                                    \\
  \end{array}
\end{equation*}

@@

\begin{equation*}
  \fontsize{7.2}{9}\selectfont
  \begin{array}{llcl}
    \restrp[n+1][\lbrack 0,p-1 \rbrack]     &
    (\fulldepscohs[n]:\fulldepscohstype[n]) & :      & \restrptype[n+1][\lbrack 0,p-1 \rbrack](\fulldepscohs.\depscohs.\fulldeps[n])) \\
    \restrp[n+1]                            &
    \fulldepscohs[n]                        & \defeq & \unittype                                                                      \\
    \restrp[n+1][\lbrack 0,p \rbrack]       &
    \fulldepscohs[n]
                                            & \defeq &
    (\restrp[n+1][\lbrack 0,p-1 \rbrack](\fulldepscohs[n]),\restrp[n+1][p](\fulldepscohs[n]))                                         \\
  \end{array}
\end{equation*}

@@

\begin{equation*}
  \fontsize{7.2}{9}\selectfont
  \begin{array}{llcl}
    \cohptype[n][\lbrack 0,p-1 \rbrack] & (\fulldepscohs[n]:\fulldepscohstype[n]) & :      & \U                                                           \\
    \cohptype[n]                        & \unitpoint                              & \defeq & \unittype                                                    \\
    \cohptype[n][\lbrack 0,p \rbrack]   & (\fulldepscohs[n])                      & \defeq & \cohptype[n][\lbrack 0,p-1 \rbrack](\fulldepscohs[n]) \times \\
                                        &                                         &        & \;\;\;\;\left\{
    \begin{array}{l}
      \Pi q \leq n-p.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega.\,\Pi d:\framep[n+2][p](\overline{\deps}(\fulldepscohs.\depscohs[n][\lbrack 0,p-1 \rbrack])).\,\Pi c:\painting[n+2][p](\overline{\fulldeps}(\fulldepscohs[n])) \\
      \fulldepscohs.\depscohs.\restrp[n][p][q][\epsilon](\restrf[n+1][p](d))(\restrp[n+1][p][r][\omega]
      (\fulldepscohs[n])(d)(c)) =                                                                                                                                                                                             \\
      \fulldepscohs.\depscohs.\restrp[n][p][r][\omega](\restrf[n+1][p](d))(\restrp[n+1][p][q+1][\epsilon]
      (\fulldepscohs[n])(d)(c))
    \end{array}
    \right.                                                                                                                                               \\
  \end{array}
\end{equation*}

@@

    \cohttype[n]                                                                             &

@@

              \Pi q \leq n - p.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega.\,\Pi \theta.\, \\

@@

      \Pi q \leq n-p.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega.                                                                          \\

@@

The last key construction we need is $\cohp[n+1][p]$ for $p \leq n+1$, which is by recursion on $n-p$:

\begin{equation*}
  \fontsize{7.2}{9}\selectfont
  \begin{array}{llcl}
    \cohp[n+1][p]                           &
    (\fulldepscoht[n]:\fulldepscohttype[n]) & :      &
    \cohptype[n+1][p](\overline{\fulldepscohs}(\fulldepscoht[n]))                                                                                             \\
    \cohp[n+1][n+1]                         &
    (\fulldepscoht[n])
                                            & \defeq & \lambda q \leq n-p.\lambda r\leq q.\lambda \epsilon.\lambda \omega.\lambda d. \lambda (l,c). l\epsilon \\
    \cohp[n+1][p \leq n]                    &
    (\fulldepscoht[n])
                                            & \defeq & \lambda q \leq n-p.\lambda r\leq q.\lambda \epsilon.\lambda \omega.\lambda d. \lambda (l,c).
    \left(\begin{array}{l}
              \cohl[n][p][q][r][\epsilon][\omega](\fulldepscoht.\depscoht[n][\lbrack 0,p-1 \rbrack])(d)(l), \\
              \cohp[n+1][p+1][q][r][\epsilon][\omega](\fulldepscoht[n])(d,l))(c)                            \\
            \end{array}\right)                                                       \\
  \end{array}
\end{equation*}

From which we can deduce $\cohp[n+1][\lbrack 0,p-1 \rbrack]$ for $p \leq n+2$ again by a second recursion, this time on $p$:
